---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# STAT545.Assignment.Package

<!-- badges: start -->
<!-- badges: end -->

STAT545.Assignment.Package aims to provide users with a function, the "count_all_missing_by_group" function. This function ought to return the number of missing observations with respect to under-specified groupings within a given data frame or tibble by way of a another tibble.

## Installation

You can install the development version of STAT545.Assignment.Package from [GitHub](https://github.com/) with the following command:

> install_github("https://github.com/stat545ubc-2025/assignment-b2-mark-liu", ref = "1.0.0")

## Example

This is a basic example which shows how the "count_all_missing_by_group" function is intended to work:

```{r example}
library(STAT545.Assignment.Package)

count_all_missing_by_group(iris)
count_all_missing_by_group(penguins, island)
count_all_missing_by_group(airquality, Month)
count_all_missing_by_group(airquality, Month, .groups = "keep")
```
